Stability in human interaction networks: sector relative sizes, prominence of topological measures and time activity statistics.

### 2015-04-29 paper.tex
arrumacoes espalhadas

%\title[Evolution of interaction networks]{On the evolution of interaction networks: primitive typology of vertex, prominence of measures and activity statistics}% Force line breaks with \\
%\title[Evolution of interaction networks]{On the evolution of interaction networks: a primitive typology of vertex}% Force line breaks with \\
\title[Stability of interaction networks]{Stability in human interaction networks: primitive typology of vertex, prominence of measures and time activity statistics}% Force line breaks with \\

@@

Let a sector to which a vertex belongs yield a type for the corresponding participant. Accordingly, a participant may be considered peripheral, intermediary or a hub. This trivial consideration raises important questions: is this typology stigmatizing or prejudice inclined in any way? What do we know about each type and about the typology itself?
These general considerations about this ``primitive'' typology will help us answer the first questions:
\begin{itemize}
	\item A participant belongs to many networks (his family, family of a friend, the email list to which he belongs, work friends, etc.).
	\item A participant might belong to all three sectors at the same time. Actually, it is reasonable to assume that almost every person belongs to all three sectors for some of the networks.
	\item The participant often transitions from one sector to another within a network.
	\item Reported stability of network structure arises from activity with continuous change of the participant types.
\end{itemize}

>>>>

%\title[Evolution of interaction networks]{On the evolution of interaction networks: primitive typology of vertex, prominence of measures and activity statistics}% Force line breaks with \\
%\title[Evolution of interaction networks]{On the evolution of interaction networks: a primitive typology of vertex}% Force line breaks with \\
\title[Stability of interaction networks]{Stability in human interaction networks: sector relative sizes, prominence of topological measures and time activity statistics.}% Force line breaks with \\

@@

Let a sector to which a vertex belongs yield a type for the corresponding participant. Accordingly, a participant may be considered peripheral, intermediary or a hub. This trivial consideration raises important questions: is this typology stigmatizing or prejudice inclined in any way? What do we know about each type and about the typology itself?
These general considerations about this ``primitive'' typology will help us answer the first questions:
\begin{itemize}
	\item A participant belongs to many networks (his family, family of a friend, the email list to which he belongs, work friends, etc.).
	\item A participant might belong to all three sectors at the same time. Actually, it is reasonable to assume that almost every person belongs to all three sectors for some of the networks.
	\item The participant often transitions from one sector to another within a network.
	\item Reported stability of network structure is concomitant with the continuous change of participants and the type of each participant.
\end{itemize}
